Gaussian Process regression for astronomical time-series

### 2022-09-07 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) got GP regression (adapted from Figure 2.3 of \citealt{} }
  \label{fig:GPR_PGM}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) for GP regression (adapted from Figure 2.3 of \citealt{RW07} given observations $\mathbf{y}$ at inputs $\mathbf{t}$, wh prediction at test input $t_\star$. Dots represent fixed variables (inputs), grey circles represent observed variables white circles represent unknown (latent) variables. The thick thick horizontal bar indicates a set of fully connected nodes.}
  \label{fig:GPR_PGM}
\end{figure}
